Exploring the Vectorization of Python Constructs Using Pythran and Boost SIMD

### 2013-11-29 doc/papers/wpmvp14/paper.tex

The typical way to solve this issue in C++ is to use \emph{expression
templates}, a technique described in~\cite{} that uses the C++ type system to
perform lazy evaluation of an expression. However, this approach is limited to
a single expression. Listing~\ref{lst:numpy-code-fs} illustrates the situation:
expression templates would not prevent the creation of temporary arrays
\texttt{t0} and \texttt{t1}. Fortunately, it is possible to apply \emph{forward
substitution} to fall-back to the expression from Listing~\ref{lst:numpy-code}
and avoid the creation of any temporary.

@@

>>>>

The typical way to solve this issue in C++ is to use \emph{expression
templates}, a technique described in~\cite{} that uses the C++ type system to
perform lazy evaluation of an expression. However, this approach is limited to
a single expression. Listing~\ref{lst:numpy-code-fs} illustrates the situation:
expression templates would not prevent the creation of temporary arrays
\texttt{t0} and \texttt{t1}. Fortunately, it is possible to apply \emph{forward
substitution} to fall-back to the expression from Listing~\ref{lst:numpy-code}
and avoid the creation of any temporary in some case detected with static analysis
of the source code.

@@

\subsection{Vectorization of \texttt{ndarray} point-to-point operations with
intermediate array}

To have good performance even with intermediate array, we use forward substitution
detect through a static analysis. It can be done only if it is not use multipe time
--- as it would lead to compute the same thing many times --- and if values used
to compute it are not changed between definition and use.
This detection transform 3 SIMD Loop computation in one intensive computation in
the case of Listing~\ref{numpy-code-fs}

    \includegraphics[width=.5\textwidth]{rosen_fs}
    \caption{Timings of rosen computation with mutlpiple assignment using CPython, Pythran, Pythran with vectorization, Pythran with vectorization and forward substitution.}
    \label{fig:numpy-timings}
